---
title: Analyzing IMDb datasets
authors: "Dirk Beekmans, Hugo Reniers, Sjors Boelaars, Parisa Vatankh, Dani Visser"
output:
  html_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(readr)
library(dplyr)
library(tidyverse)
library(ggplot2)
```

**Authors:** - Dirk Beekmans - Hugo Reniers - Sjors Boelaars - Parisa Vatankh - Dani Visser

# Introduction

This report provides an analysis of two IMDb datasets: one containing information about titles and another with ratings and votes. The datasets are described below:

## Titles

### Description

The titles dataset contains information about various titles, including movies, TV series, and more. Below are the variables included in this dataset:

-   `tconst` (string): Alphanumeric unique identifier of the title.
-   `titleType` (string): The type/format of the title (e.g., movie, short, tvseries, tvepisode, video, etc).
-   `primaryTitle` (string): The more popular title or the title used by filmmakers for promotional materials.
-   `originalTitle` (string): The original title in the original language.
-   `isAdult` (boolean): 0 for non-adult titles; 1 for adult titles.
-   `startYear` (YYYY): Represents the release year of a title. For TV series, it is the series start year.
-   `endYear` (YYYY): TV series end year. Use '\N' for all other title types.
-   `runtimeMinutes`: The primary runtime of the title in minutes.
-   `genres` (string array): Includes up to three genres associated with the title.

## Ratings and Votes Dataset

### Description

The ratings and votes dataset contains information about the ratings and votes received by titles. Here are the variables in this dataset:

-   `tconst` (string): Alphanumeric unique identifier of the title.
-   `averageRating`: Weighted average of all individual user ratings.
-   `numVotes`: The number of votes the title has received.

# Data Exploration

In this section, we'll explore both datasets to gain insights into the data.

## Titles Dataset Exploration

### Summary Statistics

Let's start by examining some summary statistics for the titles dataset:


```{r message=FALSE, warning=FALSE, include=FALSE}

titles <-read_tsv(gzfile('../../data/raw_data/title.basics.tsv.gz'))

```

```{r message=FALSE, warning=FALSE}
# Display summary statistics

summary(titles)

# Show the first few rows of data

head(titles)
```

## Ratings Dataset Exploration

### Summary Statistics

And here the summary statistics for the ratings dataset:


```{r message=FALSE, warning=FALSE, include=FALSE}

ratings <-read_tsv(gzfile('../../data/raw_data/title.ratings.tsv.gz'))

```

```{r message=FALSE, warning=FALSE}
# Display summary statistics

summary(ratings)

# Show the first few rows of data

head(ratings)
```

```{r message=FALSE, warning=FALSE, include=FALSE}

titles <- titles %>%
  mutate(Decade = as.integer(startYear) %/% 10 * 10)
```

# Data Visualization

## Historgram of release years
```{r message=FALSE, warning=FALSE}
ggplot(titles, aes(x = as.factor(Decade))) +
  geom_bar(fill = "skyblue", color = "black") +
  labs(title = "Distribution of Titles by Release Decade",
       x = "Release Decade",
       y = "Count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

