---
title: "Effect of genre on IMDB popularity score"
author: "Hugo Reniers, Dirk Beekmans, Sjors Boelaars, Parisa Vatankh, Dani Visser"
output: html_document
date: "2023-09-12"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(tidyr)
library(ggplot2)
library(readr)
library(data.table)
library(dplyr)
library(tidyverse)
```

## Introduction
  
To answer our research question, we utilized raw data from IMDB.com to collect information about the genre and average user ratings of IMDB movies. 

Included in this report is a description of the variables that are utilized in the analysis combined with summary statistics. 

**Update when project is almost finished**

The question that will be answered is: 

*'To what extend does the genre of a movie affect its average rating'*

### Dependent Variables

In here we will load the code output that we will create during the project. Visualizations for example

### Conclusion

Here we will write the conclusion
